### 2020-03-03 CalNotes.tex
Update CTL

Efficient parameter estimation for stochastic models is essential in a wide range of applications in natural and social sciences. In several areas, the data originates from phenomena which vary continuously in time and which are endowed with a multiscale structure. This is the case, for example, in molecular dynamics, oceanography and atmosphere science or in econometrics. Frequently, it is desirable in this areas to infer from data a simpler model which captures effectively large-scale structures, or slow variations, disregarding small-scale fluctuations or treating them as a source of noise. The mismatch between the data and their desired slow-scale representation is a typical instance of a problem of model misspecification, which, if ignored or mistreated, can lead to wrong solutions. Indeed, the data, coming from the full dynamics, are compatible with the coarse-grained model only at the time scales at which the effective dynamics is valid.

@@

		-\sum_{i=1}^N V_i'(x)x \leq a - bx^2.

@@

@@

\begin{remark} Let us remark that for the multiscale equation \eqref{eq:SDE_MS} one should check the condition above for the potential $V(x) + p(x/\epl)$. Nevertheless, for functions $p$ satisfying Assumption \ref{as:regularity}, the result holds trivially.
\end{remark}

@@

\begin{proof} Let us remark that in the proof of Theorem \ref{thm:mainTheorem} we showed that
	\begin{equation}
	A = \frac1\delta \E^{\rho^0}[V'(Z) \otimes V'(X)]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)],
	\end{equation}
	and
	\begin{equation}
	\E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] = - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ] \alpha + \frac1\delta \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)].
	\end{equation}
	Hence, the decomposition \eqref{eq:alphaDecomposition} yields
	\begin{equation}
	\begin{aligned}
	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = & \sqrt{T}\left( I_1^\epl(T) - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] \right) \\
	&+ \sqrt{T} \frac1\delta \left( \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \right. \\
	&\qquad \qquad \left. - \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
	&- \sqrt{T} I_2^\epl(T).
	\end{aligned}
	\end{equation}
	\corr{Third term is OK:} We rewrite the term involving $I_2^\epl(T)$ as
	\begin{equation}
	\sqrt{T} I_2^\epl(T) = \frac{\sqrt{2\sigma}}{\sqrt{T}} \widetilde M^{-1} Q^\epl_T,
	\end{equation}
	where, since $Z_t^\epl$ is adapted with respect to the natural filtration $\mathcal F_t$ of the Wiener process $W \defeq \left(W_t, t \geq 0\right)$, the quantity
	\begin{equation}
	Q^\epl_T \defeq \int_0^T V'(Z^\epl_t) \dd W_t,
	\end{equation}
	is a martingale whose quadratic variation is given by
	\begin{equation}
	\langle Q^\epl \rangle_T = \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t. 
	\end{equation}
	Since the ergodic theorem guarantees that 
	\begin{equation}
	\lim_{T\to\infty}\frac{\langle Q^\epl \rangle_T}{T} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)], \quad \text{in } L^1(\mu^\epl),
	\end{equation}
	the martingale central limit theorem gives 
	\begin{equation}
	\lim_{T\to\infty}\frac{1}{\sqrt{T}} Q^\epl_T = \Xi^\epl, \quad \text{in law},
	\end{equation}
	where $\Xi^\epl \sim \mathcal N(0, \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)])$.
	Now, by the ergodic theorem 
	\begin{equation}
	\lim_{T \to \infty} \widetilde M^{-1} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}, \quad \text{a.s.}
	\end{equation}
	Therefore, we have by Slutsky's theorem that
	\begin{equation}
	\lim_{T \to \infty} \sqrt{T} I_2^\epl(T) = \Lambda^\epl \sim \mathcal N\left(0, \Gamma^\epl\right), \quad \text{in law}.
	\end{equation}
	where the covariance matrix $\Gamma^\epl$ is given by
	\begin{equation}
		\Gamma^\epl = 2\sigma \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}\E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)]\E^{\rho^\epl}[V'(X^\epl) \otimes V'(Z^\epl)]^{-1}.
	\end{equation}
	Finally, we denote by $\Lambda$ the limit for $\epl \to 0$ of the sequence of Gaussian random variables $\Lambda^\epl$.

	\corr{Idea for the first term:} The first term can be decomposed in
	\begin{equation} \label{eq:decomposition_first_term}
	\sqrt{T}&\left( I_1^\epl(T) - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] \right) \\
	&\hspace{2cm}= \sqrt{T} \left( I_1^\epl(T) - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \frac1T \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t \right) \\
	&\hspace{2cm} \quad + \sqrt{T} \left(\E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \frac1T \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t \right. \\
	&\hspace{4cm} \left. - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] \right),
	and now we focus on its second part. Let $\mathcal L^\epl$ be the generator of the joint process $(X^\epl, Z^\epl)$, i.e.,
		\mathcal L^\epl = \begin{pmatrix} -V'(x) - \frac1\epl p'\left(\frac{x}{\epl}\right) \\ \frac1\delta (x - z)	\end{pmatrix} \cdot \nabla_{x, z} + \sigma \partial^2_{xx}.
	Then, let $\Phi_1^\epl$ the solution of the Poisson equation
		\mathcal L^\epl \Phi_1^\epl(x, z) = V'(z)\frac1\epl p'\left(\frac{x}{\epl}\right) - \E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right].
	An application of Itô formula \cite[Remark 6.17]{PaS08} yields
		\frac{1}{T} \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t = \E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right] + \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T},
	where the remainder $R_T^\epl$ is given by
		R_T^\epl \defeq \Phi_1^\epl(X^\epl_T, Z^\epl_T) - \Phi_1^\epl(X^\epl_0, Z^\epl_0),
	and $S^\epl_T$ is the martingale defined as
		S^\epl_T \defeq \int_0^T \partial_x \Phi_1^\epl(X_t^\epl, Z_t^\epl) \dd t.
%	\begin{equation}
%	\begin{aligned}
%		\sqrt{T}\left(\alpha - A + I_1^\epl(T)\right) = & \sqrt{T}\left(\alpha - A + \widetilde M^{-1}\E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right]\right)\\
%		& + \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} - \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}}.
%	\end{aligned}
%	\end{equation}
		\sqrt{T} \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} & \left( \frac1T \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t - \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] \right) \\
		&= \sqrt{T} \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \left( \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T} \right)
	Since \corr{$R^\epl_T$ is bounded independently of $\epl$}, we first get by the ergodic theorem that
%	\begin{equation}
%		\lim_{T \to \infty} \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
%	\end{equation}
		\lim_{T \to \infty} \frac{\E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
	Repeating the same reasoning as for $Q_T^\epl$, we get 
%	\begin{equation}
%		\lim_{T \to \infty} \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
%	\end{equation}
	\lim_{T \to \infty} \sqrt{2\sigma} \frac{\E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
	where the covariance is given by
		\Gamma_1^\epl = 2\sigma \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}\E^{\rho^\epl}[\partial_x \Phi_1^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi_1^\epl(X^\epl, Z^\epl)]\E^{\rho^\epl}[V'(X^\epl) \otimes V'(Z^\epl)]^{-1}.
	\corr{For the second part of \eqref{eq:decomposition_first_term} we follow a similar procedure defining a different Poisson equation. The argument has to be slightly modified because we have to work with random matrix rather than random vector, but finally we obtain a second Gaussian term $\mathcal N(0, \Gamma_2^\epl)$. Therefore, we have to study the limit as $\epl$ goes to zero of the covariance matrices $\Gamma_1^\epl$ and $\Gamma_2^\epl$, which depend on the solutions $\Phi_1^\epl$ and $\Phi_2^\epl$ of the Poisson problems.} \\

@@

\begin{proof}[Proof of Lemma \ref{lem:ergodicity}] Lemma \ref{lem:density} guarantees that the Fokker--Planck equation can be written directly from the system \eqref{eq:systemSDE}. For geometric ergodicity, let 
	\begin{equation}
	\mathcal S(x,z) \defeq \begin{pmatrix} -\sum_{i=1}^N V_i'(x) \\ \frac1\delta (x - z) \end{pmatrix} \cdot \begin{pmatrix} x \\ z \end{pmatrix} = -\sum_{i=1}^N V_i'(x)x+\frac1\delta(xz-z^2).
	\end{equation}
	Due to Assumption \ref{as:regularity}\ref{as:regularity_diss} and Young's inequality, we then have for all $\gamma > 0$
	\begin{equation}
	\mathcal S(x,z) \leq a + \left(\frac{1}{2\gamma\delta} - b\right)x^2 + \frac1\delta\left(\frac{\gamma}{2} - 1\right)z^2.
	\end{equation}
	We choose $\gamma = \gamma^* \defeq 1 - b\delta + \sqrt{1 + (1 - b\delta)^2} > 0$ so that
	\begin{equation}
	C(\gamma^*) \defeq -\frac{1}{2\gamma^*\delta} + b = -\frac1\delta\left(\frac{\gamma^*}{2} - 1\right),
	\end{equation}
	and we notice that $C(\gamma^*) > 0$ if $\delta > 1/(4b)$. In this case, we have
	\begin{equation}
	\mathcal S(x, z) \leq a - C(\gamma^*) \norm{\begin{pmatrix} x & z \end{pmatrix}^\top}^2,
	\end{equation}
	and problem \eqref{eq:systemSDE} is dissipative. The result then follows from \cite[Theorem 4.4]{MSH02}.
\end{proof}

>>>>

Efficient parameter estimation for stochastic models is essential in a wide range of applications in natural and social sciences. In several areas, the data originate from phenomena which vary continuously in time and which are endowed with a multiscale structure. This is the case, for example, in molecular dynamics, oceanography and atmosphere science or in econometrics. Frequently, it is desirable in this areas to infer from data a simpler model which captures effectively large-scale structures, or slow variations, disregarding small-scale fluctuations or treating them as a source of noise. The mismatch between the data and their desired slow-scale representation is a typical instance of a problem of model misspecification, which, if ignored or mistreated, can lead to wrong solutions. Indeed, the data, coming from the full dynamics, are compatible with the coarse-grained model only at the time scales at which the effective dynamics is valid.

@@

		-\alpha \cdot V'(x) x \leq a - bx^2.

@@

\corr{
\begin{remark}\label{rem:regularity_diss} In the following, in particular in the proof of Lemma \ref{lem:ergodicity}, we will employ Assumption \ref{as:regularity}\ref{as:regularity_diss} for the whole drift of the SDE \eqref{eq:SDE_MS}, i.e., the function 
	\begin{equation}
		V^\epl(x) \defeq \alpha \cdot V(x) - p\left(\frac{x}{\epl}\right).
	\end{equation}
	Since $p \in L^\infty$, the assumption above is sufficient for $V^\epl$ to satisfy Assumption \ref{as:regularity}\ref{as:regularity_diss} with different values for $a$ and $b$. In particular, if the condition holds for $\alpha \cdot V$ for a given $b > 0$, then one can choose a new value for the same coefficient which is arbitrarily close to the original one for $V^\epl$.
\end{remark}
}

@@

@@

\begin{proof} Let us introduce the notation
	\begin{equation}
		\mathcal M_\epl \defeq \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ], \quad \mathcal M_0 \defeq \E^{\rho^0} [ V'(Z) \otimes V'(X) ],
	\end{equation}
	and the notation
	\begin{equation}
		\mathfrak p_\epl \defeq \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ]\
	\end{equation}
	and let us remark that from the proof of Theorem \ref{thm:mainTheorem} one can deduce the equalities
	\begin{equation}\label{eq:CTL_A}
		A = \frac1\delta \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)],
	\end{equation}
	and
	\begin{equation}\label{eq:CTL_alpha}
		\alpha = \mathcal M_\epl^{-1} \left(\frac1\delta \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathfrak p_\epl \right).
	\end{equation}
	Let us furthermore remark that the decomposition \eqref{eq:alphaDecomposition} yields
	\begin{equation}
		\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \sqrt{T} \left(\alpha - A + I_1^\epl - I_2^\epl\right).
	\end{equation}
	Replacing the expression for $A$ and $\alpha$ given in \eqref{eq:CTL_A} and \eqref{eq:CTL_alpha}, we get
	\begin{equation}
	\begin{aligned}
	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) &= \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \\
	&+  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
	&- \sqrt{T} I_2^\epl(T).
	\end{aligned}
	\end{equation}
	\corr{Third term is OK:} We rewrite the term involving $I_2^\epl(T)$ as
	\begin{equation}
	\sqrt{T} I_2^\epl(T) = \frac{\sqrt{2\sigma}}{\sqrt{T}} \widetilde M^{-1} Q^\epl_T,
	\end{equation}
	where, since $Z_t^\epl$ is adapted with respect to the natural filtration $\mathcal F_t$ of the Wiener process $W \defeq \left(W_t, t \geq 0\right)$, the quantity
	\begin{equation}
	Q^\epl_T \defeq \int_0^T V'(Z^\epl_t) \dd W_t,
	\end{equation}
	is a martingale whose quadratic variation is given by
	\begin{equation}
	\langle Q^\epl \rangle_T = \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t. 
	\end{equation}
	Since the ergodic theorem guarantees that 
	\begin{equation}
	\lim_{T\to\infty}\frac{\langle Q^\epl \rangle_T}{T} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)], \quad \text{in } L^1(\mu^\epl),
	\end{equation}
	the martingale central limit theorem gives 
	\begin{equation}
	\lim_{T\to\infty}\frac{1}{\sqrt{T}} Q^\epl_T = \Xi^\epl, \quad \text{in law},
	\end{equation}
	where $\Xi^\epl \sim \mathcal N(0, \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)])$.
	Now, by the ergodic theorem 
	\begin{equation}
	\lim_{T \to \infty} \widetilde M^{-1} = \mathcal M_\epl^{-1}, \quad \text{a.s.}
	\end{equation}
	Therefore, we have by Slutsky's theorem that
	\begin{equation}
	\lim_{T \to \infty} \sqrt{T} I_2^\epl(T) = \Lambda^\epl \sim \mathcal N\left(0, \Gamma^\epl\right), \quad \text{in law}.
	\end{equation}
	where the covariance matrix $\Gamma^\epl$ is given by
	\begin{equation}
		\Gamma^\epl = 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)]\mathcal M_\epl^{-\top}.
	\end{equation}
	Finally, we denote by $\Lambda$ the limit for $\epl \to 0$ of the sequence of Gaussian random variables $\Lambda^\epl$.

	\corr{Idea for the first term:} Let us introduce the notation
	\begin{equation}
		J_1^\epl(T) \defeq \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl\right),
	\end{equation}
	and let us remark that we can rewrite
	\begin{equation} \label{eq:decomposition_first_term}
	\begin{aligned}
	J_1^\epl(T) &= \sqrt{T} \left( I_1^\epl(T) - \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\mathfrak p_\epl \right) \\
	& \quad + \sqrt{T} \left(\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} - \mathcal M_\epl^{-1}\right) \mathfrak p_\epl\\
	&\eqdef J_{1,1}^\epl(T) + J_{1,2}^\epl(T).
	\end{aligned}
	\end{equation}
	In order to treat the terms $J_{1,1}^\epl(T)$ and $J_{1,2}^\epl(T)$, we will employ a technique presented in \cite[Remark 6.17]{PaS08}. Denoting by $\mathcal L^\epl$ be the generator of the joint process $(X^\epl, Z^\epl)$, i.e.,
	\begin{equation}
		\mathcal L^\epl = -\left(V'(x) + \frac1\epl p'\left(\frac{x}{\epl}\right)\right)\partial_x + \frac1\delta (x - z) \partial_z  + \sigma \partial^2_{xx},
	\end{equation}
	let $\Phi^\epl$ the solution of the Poisson equation
	\begin{equation}\label{eq:CLT_Poisson}
		\mathcal L^\epl \Phi^\epl(x, z) = \chi(x, z) - \E^{\rho^\epl}[\chi(X^\epl, Z^\epl)].
	\end{equation}	
	where $\chi$ is a sufficiently smooth function. Then, an application of Itô formula  yields
	\begin{equation}
	\frac{1}{T} \int_0^T  \chi(X_t^\epl, Z_t^\epl) \dd t = \E^{\rho^\epl}[\chi(X^\epl, Z^\epl)] + \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T},
	\end{equation}
	where
	\begin{equation}
		R_T^\epl \defeq \Phi^\epl(X^\epl_T, Z^\epl_T) - \Phi^\epl(X^\epl_0, Z^\epl_0), \quad S^\epl_T \defeq \int_0^T \partial_x \Phi^\epl(X_t^\epl, Z_t^\epl) \dd W_t.
	\end{equation}
	Let us consider $J_{1,1}^\epl(T)$ and denote by $\Phi_1^\epl$ the solution of \eqref{eq:CLT_Poisson} with 
	\begin{equation}
		\chi(x, z) = 
	\end{equation}

	Let us first focus on $J_{1,2}^\epl(T)$. Denoting by

	Therefore, we have
%	\begin{equation}
%	\begin{aligned}
%		\sqrt{T}\left(\alpha - A + I_1^\epl(T)\right) = & \sqrt{T}\left(\alpha - A + \widetilde M^{-1}\E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right]\right)\\
%		& + \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} - \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}}.
%	\end{aligned}
%	\end{equation}
	\begin{equation}
		J_{1,1}^\epl(T)= \sqrt{T} \mathcal M_\epl^{-1} \left( \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T} \right)
	\end{equation}
	Since \corr{$R^\epl_T$ is bounded independently of $\epl$}, we first get
%	\begin{equation}
%		\lim_{T \to \infty} \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
%	\end{equation}
	\begin{equation}
		\lim_{T \to \infty} \frac{\mathcal M_\epl^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
	\end{equation}
	Repeating the same reasoning as for $Q_T^\epl$, we get 
%	\begin{equation}
%		\lim_{T \to \infty} \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
%	\end{equation}
	\begin{equation}
	\lim_{T \to \infty} \sqrt{2\sigma} \frac{\mathcal M_\epl^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
	\end{equation}
	where the covariance is given by
	\begin{equation}
		\Gamma_1^\epl = 2\sigma \mathcal M^{-1}\E^{\rho^\epl}[\partial_x \Phi_1^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi_1^\epl(X^\epl, Z^\epl)]\mathcal M^{-\top}.
	\end{equation}
	\corr{For the second part of \eqref{eq:decomposition_first_term} we follow a similar procedure defining a different Poisson equation. The argument has to be slightly modified because we have to work with random matrix rather than random vector, but finally we obtain a second Gaussian term $\mathcal N(0, \Gamma_2^\epl)$. Therefore, we have to study the limit as $\epl$ goes to zero of the covariance matrices $\Gamma_1^\epl$ and $\Gamma_2^\epl$, which depend on the solutions $\Phi_1^\epl$ and $\Phi_2^\epl$ of the Poisson problems.} \\

@@

\begin{proof}[Proof of Lemma \ref{lem:ergodicity}] Lemma \ref{lem:density} guarantees that the Fokker--Planck equation can be written directly from the system \eqref{eq:systemSDE}. For geometric ergodicity, let 
	\begin{equation}
	\mathcal S(x,z) \defeq \begin{pmatrix} -\alpha \cdot V'(x) - \frac1\epl p'(\frac{x}{\epl}) \\ \frac1\delta (x - z) \end{pmatrix} \cdot \begin{pmatrix} x \\ z \end{pmatrix} =  -\left(\alpha \cdot V'(x) + \frac1\epl p'\left(\frac{x}{\epl}\right)\right)x + \frac1\delta(xz-z^2).
	\end{equation}
	Due to Assumption \ref{as:regularity}\ref{as:regularity_diss}, Remark \ref{rem:regularity_diss} and Young's inequality, we then have for all $\gamma > 0$
	\begin{equation}
	\mathcal S(x,z) \leq a + \left(\frac{1}{2\gamma\delta} - b\right)x^2 + \frac1\delta\left(\frac{\gamma}{2} - 1\right)z^2.
	\end{equation}
	We choose $\gamma = \gamma^* \defeq 1 - b\delta + \sqrt{1 + (1 - b\delta)^2} > 0$ so that
	\begin{equation}
	C(\gamma^*) \defeq -\frac{1}{2\gamma^*\delta} + b = -\frac1\delta\left(\frac{\gamma^*}{2} - 1\right),
	\end{equation}
	and we notice that $C(\gamma^*) > 0$ if $\delta > 1/(4b)$. In this case, we have
	\begin{equation}
	\mathcal S(x, z) \leq a - C(\gamma^*) \norm{\begin{pmatrix} x & z \end{pmatrix}^\top}^2,
	\end{equation}
	and problem \eqref{eq:systemSDE} is dissipative. The result then follows from \cite[Theorem 4.4]{MSH02}.
\end{proof}
